Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-06 raspi_journal.tex
Reorganizing the document and adding basic conclusions
Edit abstract

% Abstract (Do not use inserted blank lines, i.e. \\)
\abstract{Deploying a large-scale and configurable testbed for
  networking and storage can be challenging, not only due to the
  inherent costs of the hardware, but due to maintenance challenges
  and ability to replicate results consistently. The latter requires
  not only the devices to run the same operating system (OS), but also
  have exactly the same configurations and software packages. This
  paper presents the design, step-by-step setup, and configuration of
  an inexpensive testbed using Raspberry Pi devices for networking
  (wireless or wired) and storage applications, although the
  architecture can be used for other applications that require
  replicable results.  Specifically, we provide an in-depth
  performance evaluation for network coding, a new paradigm in
  networking and storage, and demonstrating the processing
  capabilities and energy behaviour of various code constructions and
  algorithms over different Raspberry Pi models. Our results show that
  processing speeds of more than 80 Mbps and 800 Mbps are attainable
  for a wide array of configurations are attainable for the Raspberry
  Pi Model 1 and 2, respectively, and that processing energy per bit for
  network coding is below 1 nJ in a large regime and even an order
  of magnitude lower for some algorithms.}

@@

% \section{Topologies}
% \input{topologies}

@@

\section{Measurements}
\input{measurements}

@@

\section{Conclusion}
\label{sec:conclusions}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

>>>>

% Abstract (Do not use inserted blank lines, i.e. \\)
\abstract{Deploying a large-scale and configurable testbed for
  networking and storage can be challenging, not only due to the
  inherent costs of the hardware, but due to maintenance challenges
  and ability to replicate results consistently. The latter requires
  not only the devices to run the same operating system (OS), but also
  have exactly the same configurations and software packages. This
  paper presents the design, step-by-step setup, and configuration of
  an inexpensive testbed using Raspberry Pi devices for networking
  (wireless or wired) and storage applications, although the
  architecture can be used for other applications that require
  replicable results.  Specifically, we provide an in-depth
  performance evaluation for network coding, a new paradigm in
  networking and storage, and demonstrating the processing
  capabilities and energy behaviour of various code constructions and
  algorithms over different Raspberry Pi models. Our results show that
  processing speeds of more than 80 Mbps and 800 Mbps are attainable
  for a wide array of configurations for the Raspberry Pi Model 1 and
  2, respectively, and that processing energy per bit for network
  coding is below 1 nJ in a large regime and even an order of
  magnitude lower for some algorithms.}

@@

@@

\section{Measurements and Discussion}
\input{measurements}

\section{Conclusion}
\input{conclusions}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Materials and Methods}
